### 2023-12-08 main.tex
expectation

On one hand, this absorbing duality allows to write the non-equilibrium steady state in terms of these absorption probabilities and then
one can deduce macroscopic properties. For instance this sufficed in  \cite{KMP} to prove local equilibrium for the KMP model.
On the other hand, absorption probabilities are hard to compute explicitly since they fulfill difference equation with proper boundary conditions. 
The situation simplifies for a chain with two reservoirs on the boundary sites. 
In this context, the integrable structure of the process can be combined with duality. As shown in \cite{frassek2020eigenstates,frassek2020duality}, this approach leads to closed-form expressions for the correlations and the non-equilibrium steady state.

@@

@@

	\langle q_{1},\ldots,q_{N-1}|\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}\rangle=\prod_{a=1}^{N-1}\delta_{\xi_{a}^{u(x)},q_{a}}

@@

@@

In \eqref{absProbabilitiesIntegrable} the variable $t_k$ is $1$ (resp. $0$) when the dual particle of species $a_k$ initially positioned at site $x_{k}$ is absorbed at at the extra site $\{0\}$ (resp. $\{L+1\}$).

@@

@@

{\color{blue}where the expectation is taken with respect to the non-equilibrium steady state distribution, then it is given in \eqref{exactCorrelations}.}

@@

@@

&\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_x=\tau_{x}\}}\right)\left(\prod_{x=1\,:\,\tau_{x}=N}^{L}\left(1-\sum_{a_{x}=1}^{N-1}\mathbbm{1}_{\{Y_x=a_{x}\}}\right)\right)\nonumber\\

@@

Therefore, using the linearity of the expectation and introducing the index $b\in \{0,\ldots,L\}$ {\color{blue} we rewrite the sum in equation \eqref{sum} as} \eqref{implicit-mass-function}.{\color{blue} Indeed, when $b>L-\ell$ we have vanishing terms in the sum \eqref{implicit-mass-function}.}

@@

where $\mathcal{P}_{x_1}(1)$ is the probability that a single random walk started at $x_1$ is absorbed in $\{0\}$.\todo{site 0?} Then, using \eqref{exactCorrelations}, we have

@@

Observing now that $c_{x}(1-\delta_{\tau_{x},N})$ can be replaced by  $c_{x}-\delta_{\tau_{x},N}$, we finally have
\begin{equation}\label{elementsABS}
	\begin{split}
		\Psi^{'}(\bm{\tau})=\frac{1}{(L+1)!}\sum_{c_{1}=\delta_{\tau_{1},N}}^{1}\ldots\sum_{c_{L}=\delta_{\tau_{L},N}}^{1}\prod_{x=1}^{L}(\alpha_{\tau_{x}}-\beta_{\tau_{x}})^{1-c_{x}}\left(1+\sum_{j=x}^{L}c_{j}\right)\beta_{\tau_{x}}^{c_{x}-\delta_{\tau_{x},N}}\dt
	\end{split}
\end{equation} 
\begin{flushright}
    $\square$
\end{flushright}
\begin{remark} By changing the summation indices from $c_x\in \{\delta_{\tau_{x},N},1\}$ to $c_{x}^{'}\in \{0,1-\delta_{\tau_{x},N}\}$ and by  the fact that occupation of each site is bounded by $1$ we rewrite \eqref{ABS} as 
\begin{equation}\label{ABS_1}
	\Psi^{'}(\bm{\tau})=\sum_{c^{'}_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c^{'}_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{(L+1-\sum_{x=1}^{L}c^{'}_{x})!}{(L+1)!}\prod_{x=1}^{L}\left((\alpha_{\tau_{x}}-\beta_{\tau_{x}})\left(2+L-x-\sum_{j=x}^{L}c^{'}_{j}\right)\right)^{c^{'}_{x}}\beta_{\tau_{x}}^{(1-c^{'}_{x}-\delta_{\tau_{x},N})}
\end{equation}
where we used the fact that 
\begin{equation}
	\left(1+\sum_{j=x}^{L}c_{j}\right) =\left(2+L-x-\sum_{j=x}^{L}c^{'}_{j}\right)\dt
\end{equation}
Equation \eqref{ABS_1} will be useful in the following. 
\end{remark}
\subsubsection{Closed formula for correlations}\label{correlation-section}
We consider $m\in \{1,\ldots,L\}$ sites with coordinates $x_{1},\ldots,x_{m}\in \{1,\ldots,L\}$ such that $x_{k}<x_{k+1}$ for all $k\in \{1,\ldots,m-1\}$. We fix $a_{k}\in\{1,\ldots,N-1\}$ and we would like to compute
\begin{equation}
	\mathbb{E}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{Y_{x_{k}}=a_{k}\}}\right]=\sum_{\bm{\tau}\in \Omega^{'}}\left(\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right)\langle\bm{\tau}|\Psi\rangle\dt%=\sum_{\bm{\tau}\in \Omega^{'}}\left(\prod_{i=1}^{m}\mathbbm{1}_{\{\tau_{y_{i}}=s_{i}\}}\right)\Psi(\bm{\tau})
\end{equation}
We fix the dual configuration $\bm{\xi}=\sum_{k=1}^{m}\delta_{a_{k}}^{x_{k}}$, corresponding to a vector $|\bm{\xi}\rangle$, and we have 
\begin{equation}
	\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}=D(\bm{\tau},\bm{\xi})\dt
\end{equation}
Thus it follows that 
\begin{align}
	\mathbb{E}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{Y_{x_{k}}=a_{k}\}}\right]=&\sum_{\bm{\tau}\in \Omega^{'}}D(\bm{\tau},\bm{\xi})\langle\bm{\tau}|\Psi\rangle
	=\sum_{\bm{\tau}\in \Omega^{'}}\langle \bm{\tau}|D|\bm{\xi}\rangle\langle\bm{\tau}|\Psi\rangle\dt
\end{align}
We denote by $|\hat{\bm{\xi}}\rangle=|\xi^{1},\ldots,\xi^{L}\rangle$, i.e. the vector constructed from $|\bm{\xi}\rangle$ by removing the components at sites $\{0\}$ and $\{L+1\}$. Recalling that {\color{blue} in the case $\nu=1$, since the matrix $R_{x}$ defined in \eqref{Revmatrix} reduces to the identity, we have that the matrix $d_{x}$ defined in \eqref{bulkElementDualityMatrix} becomes
\begin{equation}
	d_{x}=\exp{(\sum_{a=1}^{N-1}e_{aN}^{x})}
	\end{equation} then the following holds}
\begin{equation}
	S_{1}^{T}=\prod_{x=1}^{L}d_{x}
\end{equation} 
\todo{double check and ref to $d_x$ and say that R is id}
{\color{blue}As a consequence we have that }
\begin{equation}
	\langle \bm{\tau}|S_{1}^{T}|\hat{\bm{\xi}}\rangle=\langle \bm{\tau}|D|\bm{\xi}\rangle \dt
\end{equation}
Therefore, it follows that, using the resolution of the identity
\begin{align}
\label{corr-psi1}
	\mathbb{E}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{Y_{x_{k}}=a_{k}\}}\right]=& \sum_{\bm{\tau}\in \Omega^{'}}\langle \bm{\tau}|D|\bm{\xi}\rangle\langle\bm{\tau}|\Psi\rangle
	=\sum_{\bm{\tau}\in \Omega^{'}}\langle \bm{\tau}|S_{1}^{T}|\hat{\bm{\xi}}\rangle\langle\bm{\tau}|\Psi\rangle\nonumber\\
	=&\sum_{\bm{\tau}\in \Omega^{'}}\langle \hat{\bm{\xi}}|S_{1}|\bm{\tau}\rangle\langle\bm{\tau}|\Psi\rangle
	=\langle \hat{\bm{\xi}}|S_{1}|\Psi\rangle
	=\langle \hat{\bm{\xi}}|\Psi^{'}\rangle\dt
\end{align}

@@

\begin{remark} 
Without using duality but only  the definition $|\Psi^{'}\rangle=S_1|\Psi\rangle$ and that
\begin{equation}
 \langle \tau |S_1=\begin{cases}
                    \sum_{\sigma=1}^N\langle \sigma|  \quad\text{if}\quad \tau=N\\
                    \langle \tau| \quad\text{else} 
                   \end{cases}\,,
\end{equation} 
  we immediately verify 
\begin{equation}\label{eq:EE}
\begin{split}
\mathbb{E}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{Y_{x_{k}}=a_{k}\}}\right]=\sum_{\bm{\tau}\in\Omega^{'}}\prod_{k=1}^{m}\delta_{{{\tau}_{x_k}},a_{k}}\langle \bm{\tau}|\Psi\rangle=
\langle N,\ldots,N,a_1,N,\ldots,N,a_m,N,\ldots,N|\Psi^{'}\rangle\dt
 \end{split}
\end{equation} 
Here the entries $a_i\neq N$ in \eqref{eq:EE} are at position $x_i$. 
\end{remark}

@@

\subsubsection{Steady state}\label{appB}
By the knowledge of the closed formula for correlations \eqref{exactCorrelations}, we find the probability mass-function in the non-equilibrium steady state by using Corollary~\ref{Corollary-NESS-ABS}. Indeed we show here that 
$|\Psi\rangle=S_{1}^{-1}|\Psi^{'}\rangle$ is nothing but Corollary~\ref{Corollary-NESS-ABS}.
On a single site we have that 
\begin{equation}\label{S1-L1}
	\mathcal{S}_{1}^{-1}=\mathbbm{1}+(-1)\sum_{a=1}^{N-1}e_{Na}
\end{equation}
thus,
\begin{equation}
	\mathcal{S}_{1}^{-1}|\sigma\rangle=|\sigma\rangle+(-1)(1-\delta_{\sigma,N})|N\rangle
\end{equation}
By taking the tensor product over the chain we obtain 
\begin{equation}
	S_{1}^{-1}|\bm{\sigma}\rangle=\left(|\sigma_{1}\rangle+(-1)(1-\delta_{\sigma_{1},N})|N\rangle\right)\otimes \ldots \otimes \left(|\sigma_{L}\rangle+(-1)(1-\delta_{\sigma_{L},N})|N\rangle\right)
\end{equation}
therefore, projecting on $\langle \bm{\tau}|$ we have
\begin{equation}\label{Tensor-S1}
	\langle \bm{\tau}|	S_{1}^{-1}|\bm{\sigma}\rangle=\prod_{x=1}^{L}\left(\delta_{\tau_{x},\sigma_{x}}+(-1)\delta_{\tau_{x},N}\sum_{a_{x}=1}^{N-1}\delta_{\sigma_{x},a_{x}}\right)\dt
\end{equation}

@@

			\langle \bm{\tau}|S_{1}^{-1}|\Psi^{'}\rangle=&\sum_{\bm{\sigma}\in \Omega^{'}}\Psi^{'}(\bm{\sigma})\prod_{x=1}^{L}\left(\delta_{\tau_{x},\sigma_{x}}+(-1)\delta_{\tau_{x},N}\sum_{a_{x}=1}^{N-1}\delta_{\sigma_x,a_{x}}\right)\nonumber\\
			=&\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\sum_{\bm{\sigma}\in \Omega^{'}}\Psi^{'}(\bm{\sigma})\left(\prod_{x=1\,:\,x\notin\{q_{1},\ldots,q_{b}\}}^{L}\delta_{\tau_{x},\sigma_x}\right)\left(\prod_{x\in \{q_{1},\ldots,q_{b}\}}\delta_{\tau_{x},N}\sum_{a_{x}=1}^{N-1}\delta_{\sigma_{x},a_{x}}\right)\nonumber\\
			=&\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{a_{q_{1}},\ldots a_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{a_{q_{1}}}_{q_{1}},\ldots,\underbrace{a_{q_{b}}}_{q_{b}},\ldots,\tau_{L})

@@

		where the notation

@@

			\Psi^{'}(\tau_{1},\ldots,\underbrace{a_{q_{1}}}_{q_{1}},\ldots,\underbrace{a_{q_{b}}}_{q_{b}},\ldots,\tau_{L})
		means that, for all $b\in \{0,\ldots,L\}$ and for all $1\leq q_{1}<\ldots<q_{b}\leq L$,
				\tau_{x}=a_{x}\qquad &\text{if}\quad x\in\{q_{1},\ldots,q_{b}\}\\
				\tau_{x}=\tau_{x}\qquad &\text{if}\quad \text{otherwise}

@@

		In the second equality we have rewritten the product by introducing the summation over $b$, the coordinates $q_{1},\ldots,q_{b}$ and the occupations variables $a_{q_{1}},\ldots,a_{q_{k}}$. In the last equality we have summed over all possible $\bm{\sigma}\in \Omega^{'}$. Finally, using equation \eqref{interpretation-PsiP}, the result follows. 

@@

The computations made for the multispecies stirring process can be specialized to the single-species case $N=2$. In this situation we retrieve the SSEP, that was studied using the same approach as presented here in \cite{frassek2020eigenstates}. We report the Hamiltonians and the similarity transformations of SEEP: 

@@

	\sum_{c_{1}\ldots,c_{m}=0}^{m}\frac{(L+1-\sum_{k=1}^{m}c_{k})!}{(L+1)!}\prod_{k=1}^{m}\left(2+L-x_{k}-\sum_{j=k}^{m}\right)=\sum_{q=0}^{m}\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq L}\prod_{k=1}^{q}\frac{(1+L-x_{\ell_{k}}-q+k)}{(2+L-k)}

@@

where $\mathcal{L}_{x,x+1}$ is given by \eqref{Generator} and where the boundary generators $\widetilde{\mathcal{L}}_{\text{left}}$ and $\widetilde{\mathcal{L}}_{\text{right}}$ are given in \eqref{siteDualGenerator}: they absorb particles from sites $\{1\}$ and $\{L\}$ and put them at extra-sites $\{0\}$ and $\{L+1\}$ respectively. The duality function reads is \eqref{dualityElements} specified on the chain. 

@@

are the absorption probabilities for the non-integrable chain, i.e. the probabilities that $t_{a}$ particles of species $a$ are absorbed at $\{0\}$. Here we have denoted $|\xi_{a}|=\sum_{x=1}^{L}\xi_{a}^{x}$.

>>>>

On one hand, this absorbing duality allows to write the non-equilibrium steady state in terms of these absorption probabilities and then
one can deduce macroscopic properties. For instance this sufficed in  \cite{KMP} to prove local equilibrium for the KMP model.
On the other hand, absorption probabilities are hard to compute explicitly since they fulfill difference equation with proper boundary conditions. 
The situation simplifies {\color{blue} for the simple symmetric exclusion process \cite{schutzSandow} on the geometry of } a chain with two reservoirs on the boundary sites. 
{\color{blue}In this context, the process posses an integrable structure \cite{schutzManyBody,SSEPReviewRagoucy}. This integrability property can be combined with duality to compute absorption probabilities}. As shown in \cite{frassek2020eigenstates,frassek2020duality}, this approach leads to closed-form expressions for the correlations and the non-equilibrium steady state.

@@

\begin{equation}\label{row-dual-vectors}

@@

	\langle q_{1}^{u(x)},\ldots,q^{u(x)}_{N-1}|\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}\rangle=\prod_{a=1}^{N-1}\delta_{\xi_{a}^{u(x)},q_{a}}

@@

{\color{blue} \begin{remark}
	In the following, with a slightly abuse of notation, we denote the configuration vectors on the extra-site $u(x)$ by $|\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}\rangle$. This allows to recall that these vectors belongs to the extra-space $N_{0}^{N-1}$ "attached" to original configuration space $\Omega$. Moreover, this notation allows to directly connect the ket-vector $|\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}\rangle$ with the row vector $(\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)})$ defined in \eqref{row-dual-vectors}.
\end{remark}}

@@

In \eqref{absProbabilitiesIntegrable} the variable $t_k$ is $1$ (resp. $0$) when the dual particle of species $a_k$ initially positioned at site $x_{k}$ is absorbed at at the extra site $0$ (resp. $L+1$).

@@

{\color{blue}By using the correlations in the non-equilibrium steady state \eqref{exactCorrelations}, it is possible to determine the non-equilibrium steady probability distribution. }

@@

{\color{blue}where the expectation is taken with respect to the non-equilibrium steady state, then it computed by using the correlations of equation \eqref{exactCorrelations}.}

@@

{\color{blue} The quantity $\mu(\bm{\tau})$ gives the probability, under the non-equilibrium steady distribution, of having a configuration $\bm{\tau}$, that can be composed by particles and holes as well. However, from Corollary \ref{Corolollary-ABS_Corr-abstract}, we only have an explicit formula for the expectations of the indicator of particle configurations (indeed $a_{1},\ldots,a_{m}$ are different from $N$). Therefore, to write the probability mass function $\mu$ for occupations containing holes we have to use the conservation of probability to get rid of the indicators of these holes. Then, equation \eqref{implicit-mass-function} is derived (for details see below the proof of Corollary \ref{Corollary-NESS-ABS}).\\
 The expectation on the right-hand-side of \eqref{implicit-mass-function} contains only indicators of particles configurations: indeed in the first product  $\tau_{x}\neq N$ are considered, while in the second product we have $a_{k}\neq N$ for all $k\in\{1,\ldots,N\}$. As a consequence, we can map the coordinates $x_{1},\ldots,x_{m}$ and the types $a_{1},\ldots,a_{m}$ introduced in Corollary \ref{Corolollary-ABS_Corr-abstract} with, respectively, the coordinates $x$ (where the $\tau_{x}\neq N$) and $q_{1},\ldots,q_{b}$ and with the types $\tau_{x}\neq N$ and $a_{1},\ldots,a_{b}$. For this reason, by knowing the correlations \eqref{exactCorrelations}, the probability mass function $\mu(\bm{\tau})$ given in equation \eqref{implicit-mass-function} is obtained.}\\

@@

&\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_x=\tau_{x}\}}\right)\left(\prod_{x=1\,:\,\tau_{x}=N}^{L}\left(1-\sum_{a=1}^{N-1}\mathbbm{1}_{\{Y_x=a\}}\right)\right)\nonumber\\

@@

Therefore, using the linearity of the expectation and introducing the index $b\in \{0,\ldots,L\}$ {\color{blue} we rewrite the sum in equation \eqref{sum} as} \eqref{implicit-mass-function}. {\color{blue} Indeed, when $b>L-\ell$ we have vanishing terms in the sum \eqref{implicit-mass-function}.}

@@

where $\mathcal{P}_{x_1}(1)$ is the probability that a single random walk started at $x_1$ is absorbed in $0$.\todo{site 0?} Then, using \eqref{exactCorrelations}, we have

@@

Observing now that $c_{x}(1-\delta_{\tau_{x},N})$ can be replaced by  $c_{x}-\delta_{\tau_{x},N}$, we finally have
\begin{equation}\label{elementsABS}
	\begin{split}
		\Psi^{'}(\bm{\tau})=\frac{1}{(L+1)!}\sum_{c_{1}=\delta_{\tau_{1},N}}^{1}\ldots\sum_{c_{L}=\delta_{\tau_{L},N}}^{1}\prod_{x=1}^{L}(\alpha_{\tau_{x}}-\beta_{\tau_{x}})^{1-c_{x}}\left(1+\sum_{j=x}^{L}c_{j}\right)\beta_{\tau_{x}}^{c_{x}-\delta_{\tau_{x},N}}\dt
	\end{split}
\end{equation} 
\begin{flushright}
    $\square$
\end{flushright}
\begin{remark} By changing the summation indices from $c_x\in \{\delta_{\tau_{x},N},1\}$ to $c_{x}^{'}\in \{0,1-\delta_{\tau_{x},N}\}$ and by  the fact that occupation of each site is bounded by $1$ we rewrite \eqref{ABS} as 
\begin{equation}\label{ABS_1}
	\Psi^{'}(\bm{\tau})=\sum_{c^{'}_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c^{'}_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{(L+1-\sum_{x=1}^{L}c^{'}_{x})!}{(L+1)!}\prod_{x=1}^{L}\left((\alpha_{\tau_{x}}-\beta_{\tau_{x}})\left(2+L-x-\sum_{j=x}^{L}c^{'}_{j}\right)\right)^{c^{'}_{x}}\beta_{\tau_{x}}^{(1-c^{'}_{x}-\delta_{\tau_{x},N})}
\end{equation}
where we used the fact that 
\begin{equation}
	\left(1+\sum_{j=x}^{L}c_{j}\right) =\left(2+L-x-\sum_{j=x}^{L}c^{'}_{j}\right)\dt
\end{equation}
Equation \eqref{ABS_1} will be useful in the following. 
\end{remark}
\subsubsection{Closed formula for correlations}\label{correlation-section}
We consider $m\in \{1,\ldots,L\}$ sites with coordinates $x_{1},\ldots,x_{m}\in \{1,\ldots,L\}$ such that $x_{k}<x_{k+1}$ for all $k\in \{1,\ldots,m-1\}$. We fix $a_{k}\in\{1,\ldots,N-1\}$ and we would like to compute
\begin{equation}
	\mathbb{E}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{Y_{x_{k}}=a_{k}\}}\right]=\sum_{\bm{\tau}\in \Omega^{'}}\left(\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right)\langle\bm{\tau}|\Psi\rangle\dt%=\sum_{\bm{\tau}\in \Omega^{'}}\left(\prod_{i=1}^{m}\mathbbm{1}_{\{\tau_{y_{i}}=s_{i}\}}\right)\Psi(\bm{\tau})
\end{equation}
We fix the dual configuration $\bm{\xi}=\sum_{k=1}^{m}\delta_{a_{k}}^{x_{k}}$, corresponding to a vector $|\bm{\xi}\rangle$, and we have 
\begin{equation}
	\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}=D(\bm{\tau},\bm{\xi})\dt
\end{equation}
Thus it follows that 
\begin{align}
	\mathbb{E}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{Y_{x_{k}}=a_{k}\}}\right]=&\sum_{\bm{\tau}\in \Omega^{'}}D(\bm{\tau},\bm{\xi})\langle\bm{\tau}|\Psi\rangle
	=\sum_{\bm{\tau}\in \Omega^{'}}\langle \bm{\tau}|D|\bm{\xi}\rangle\langle\bm{\tau}|\Psi\rangle\dt
\end{align}
We denote by $|\hat{\bm{\xi}}\rangle=|\xi^{1},\ldots,\xi^{L}\rangle$, i.e. the vector constructed from $|\bm{\xi}\rangle$ by removing the components at sites $0$ and $L+1$. Recalling that {\color{blue} in the case $\nu=1$, since the matrix $R_{x}$ defined in \eqref{Revmatrix} reduces to the identity, we have that the matrix $d_{x}$ defined in \eqref{bulkElementDualityMatrix} becomes
\begin{equation}
	d_{x}=\exp{(\sum_{a=1}^{N-1}e_{aN}^{x})}
	\end{equation} then the following holds}
\begin{equation}
	S_{1}^{T}=\prod_{x=1}^{L}d_{x}
\end{equation} 
\todo{double check and ref to $d_x$ and say that R is id}
{\color{blue}As a consequence we have that }
\begin{equation}
	\langle \bm{\tau}|S_{1}^{T}|\hat{\bm{\xi}}\rangle=\langle \bm{\tau}|D|\bm{\xi}\rangle \dt
\end{equation}
Therefore, it follows that, using the resolution of the identity
\begin{align}
\label{corr-psi1}
	\mathbb{E}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{Y_{x_{k}}=a_{k}\}}\right]=& \sum_{\bm{\tau}\in \Omega^{'}}\langle \bm{\tau}|D|\bm{\xi}\rangle\langle\bm{\tau}|\Psi\rangle
	=\sum_{\bm{\tau}\in \Omega^{'}}\langle \bm{\tau}|S_{1}^{T}|\hat{\bm{\xi}}\rangle\langle\bm{\tau}|\Psi\rangle\nonumber\\
	=&\sum_{\bm{\tau}\in \Omega^{'}}\langle \hat{\bm{\xi}}|S_{1}|\bm{\tau}\rangle\langle\bm{\tau}|\Psi\rangle
	=\langle \hat{\bm{\xi}}|S_{1}|\Psi\rangle
	=\langle \hat{\bm{\xi}}|\Psi^{'}\rangle\dt
\end{align}

@@

\begin{remark} 
Without using duality but only  the definition $|\Psi^{'}\rangle=S_1|\Psi\rangle$ and that
\begin{equation}
 \langle \tau |S_1=\begin{cases}
                    \sum_{\sigma=1}^N\langle \sigma|  \quad\text{if}\quad \tau=N\\
                    \langle \tau| \quad\text{else} 
                   \end{cases}\,,
\end{equation} 
  we immediately verify 
\begin{equation}\label{eq:EE}
\begin{split}
\mathbb{E}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{Y_{x_{k}}=a_{k}\}}\right]=\sum_{\bm{\tau}\in\Omega^{'}}\prod_{k=1}^{m}\delta_{{{\tau}_{x_k}},a_{k}}\langle \bm{\tau}|\Psi\rangle=
\langle N,\ldots,N,\underbrace{a_1}_{x_{1}},N,\ldots,N,\underbrace{a_m}_{x_{m}},N,\ldots,N|\Psi^{'}\rangle\dt
 \end{split}
\end{equation} 
{\color{blue}Here the notation means that the entries $a_k\neq N$ in \eqref{eq:EE} are at position $x_k$ for $k\in\{1,\ldots,m\}$.} 
\end{remark}

@@

\subsubsection{Steady state}\label{appB}
By the knowledge of the closed formula for correlations \eqref{exactCorrelations}, we find the probability mass-function in the non-equilibrium steady state by using Corollary~\ref{Corollary-NESS-ABS}. Indeed we show here that 
$|\Psi\rangle=S_{1}^{-1}|\Psi^{'}\rangle$ is nothing but Corollary~\ref{Corollary-NESS-ABS}.
On a single site we have that 
\begin{equation}\label{S1-L1}
	\mathcal{S}_{1}^{-1}=\mathbbm{1}+(-1)\sum_{a=1}^{N-1}e_{Na}
\end{equation}
thus,
\begin{equation}
	\mathcal{S}_{1}^{-1}|\sigma\rangle=|\sigma\rangle+(-1)(1-\delta_{\sigma,N})|N\rangle
\end{equation}
By taking the tensor product over the chain we obtain 
\begin{equation}
	S_{1}^{-1}|\bm{\sigma}\rangle=\left(|\sigma_{1}\rangle+(-1)(1-\delta_{\sigma_{1},N})|N\rangle\right)\otimes \ldots \otimes \left(|\sigma_{L}\rangle+(-1)(1-\delta_{\sigma_{L},N})|N\rangle\right)
\end{equation}
therefore, projecting on $\langle \bm{\tau}|$ we have
\begin{equation}\label{Tensor-S1}
	\langle \bm{\tau}|	S_{1}^{-1}|\bm{\sigma}\rangle=\prod_{x=1}^{L}\left(\delta_{\tau_{x},\sigma_{x}}+(-1)\delta_{\tau_{x},N}\sum_{a=1}^{N-1}\delta_{\sigma_{x},a}\right)\dt
\end{equation}

@@

			\langle \bm{\tau}|S_{1}^{-1}|\Psi^{'}\rangle=&\sum_{\bm{\sigma}\in \Omega^{'}}\Psi^{'}(\bm{\sigma})\prod_{x=1}^{L}\left(\delta_{\tau_{x},\sigma_{x}}+(-1)\delta_{\tau_{x},N}\sum_{a=1}^{N-1}\delta_{\sigma_x,a}\right)\nonumber\\
			=&\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\sum_{\bm{\sigma}\in \Omega^{'}}\Psi^{'}(\bm{\sigma})\left(\prod_{x=1\,:\,x\notin\{q_{1},\ldots,q_{b}\}}^{L}\delta_{\tau_{x},\sigma_x}\right)\left(\prod_{x\in \{q_{1},\ldots,q_{b}\}}\delta_{\tau_{x},N}\sum_{a=1}^{N-1}\delta_{\sigma_{x},a}\right)\nonumber\\
			=&\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{a_{1},\ldots a_{b}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{a_{1}}_{q_{1}},\ldots,\underbrace{a_{b}}_{q_{b}},\ldots,\tau_{L})

@@

			{\color{blue}In the second equality we have rewritten the product by introducing the summation over $b$, the coordinates $q_{1},\ldots,q_{b}$ and the occupations variables $a_{1},\ldots,a_{b}$. In the last equality we have summed over all possible $\bm{\sigma}\in \Omega^{'}$, taking into account the Kronecker deltas.} Here, the notation

@@

			\Psi^{'}(\tau_{1},\ldots,\underbrace{a_{1}}_{q_{1}},\ldots,\underbrace{a_{b}}_{q_{b}},\ldots,\tau_{L})
		means that, for all $b\in \{0,\ldots,L\}$ and for all $1\leq q_{1}<\ldots<q_{b}\leq L$ {\color{blue} at sites $q_{k}$ for $k=1,\ldots,b$ we have a particle of type $a_{k}$, while at the other sites ($x\notin\{q_{1},\ldots,q_{b}\}$) the occupation $\tau_{x}$ is left unchanged. }

@@

	 %Finally, using equation \eqref{interpretation-PsiP}, the result follows. 

@@

The computations made for the multispecies stirring process can be specialized to the single-species case $N=2$, {\color{blue}i.e. when only a type of particles and the holes are present.} In this situation we retrieve the SSEP, that was studied using the same approach as presented here in \cite{frassek2020eigenstates}. We report the Hamiltonians and the similarity transformations of SEEP: 

@@

	\sum_{c_{1}\ldots,c_{m}=0}^{m}\frac{(L+1-\sum_{k=1}^{m}c_{k})!}{(L+1)!}\prod_{k=1}^{m}\left(2+L-x_{k}-\sum_{j=k}^{m}c_{j}\right)=\sum_{q=0}^{m}\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq L}\prod_{k=1}^{q}\frac{(1+L-x_{\ell_{k}}-q+k)}{(2+L-k)}

@@

where $\mathcal{L}_{x,x+1}$ is given by \eqref{Generator} and where the boundary generators $\widetilde{\mathcal{L}}_{\text{left}}$ and $\widetilde{\mathcal{L}}_{\text{right}}$ are given in \eqref{siteDualGenerator}: they absorb particles from sites $\{1\}$ and $\{L\}$ and put them at extra-sites $0$ and $L+1$ respectively. The duality function reads is \eqref{dualityElements} specified on the chain. 

@@

are the absorption probabilities for the non-integrable chain, i.e. the probabilities that $t_{a}$ particles of species $a$ are absorbed at $0$. Here we have denoted $|\xi_{a}|=\sum_{x=1}^{L}\xi_{a}^{x}$.
